---
title: "Exam"
author: "Demi Bankers" "1279388"
output: html_notebook
---

# Introduction

The exam consists of 2 parts. In the first part, you have to run a regression, test if the assumptions of a linear regression model are met, and make 2 graphs.

In the second part of the exam, you will have to make a map of Catholic and Protestant schools in the Netherlands.

# Packages

```{r}
library(tidyverse)
library(gvlma)
```

# Assignment 1

## Data

The data are given:

```{r}
set.seed(123)
df1 <- as.data.frame(matrix(runif(1*50, min = 1, max = 10), ncol = 1)) %>%
    mutate(epsilon = rnorm(50, mean = 0, sd = 2)) %>%
    mutate(response = 3 - 2* V1  + epsilon) %>%
    mutate(group = ifelse(V1 <= 5, 1,2))

```

## Asignment 1a

The first assigment is to make boxplot using ggplot with group on the x-axis and V1 on the y-axis.

```{r}
ggplot(data=df1, aes(x=group, group=group, y=V1))+geom_boxplot()
```
```{r}
#We applied what we learned in the tutorials, we used ggplot and geom_boxplot to present a boxplotgraph. Df1 represents the data we used. Aes represents the aesthetics specifically the x and y label. To display them better we used group=group
```



## Assignment 1b

Run a regression with response variable as a function of V1.
Show the summary statistics of the regression.

```{r}
regression <- lm(data=df1, response ~ V1)
summary(regression)
```

check if the assumptions of linear regression are met with the `gvlma()` function.

```{r}
gvlma(regression)
```

```{r}
# we put regression in the gvlma function to check if the assumptions of a good linear regression were met with the function
```

## Assignment 1c

Make a scatterplot with:

* V1 on the x-axis and the response on the y-axis
* Include the regression line in red with confidence interval 
* In a classic theme
* The x-axis should be labeled "Predictor", the y-axis should be labeled ("Response")


```{r}
ggplot(data=regression, aes(x = V1, y = response)) + geom_point() + theme_classic() + xlab("Predictor") + ylab("Response") + geom_smooth(data=regression, method=lm, color="red")


```

```{r}
#we used gglplot and geompoint to show a scatterplot of the data regression. Again aes shows the aesthetics and x and y represent the labels.
```




# Assigment 2

# Packages

```{r}
install.packages("../Downloads//thematicmaps_2.1.tar.gz", repos = NULL, type = "source")
library(thematicmaps)
library(tidyverse)

```

## Assignment 2a

First you have to read in the file "nld_municipal_map.csv".
Hint: Look at the notebook of week 6 about maps.

```{r}
map_municipal <- read.csv2("..//Downloads/nld_municipal_map.csv", stringsAsFactors = FALSE, dec = ".")
head(map_municipal)
```

```{r}
#we used read.csv2 to read the file nld_municipal_map.csv. We used head to show the first 6 elements.
```

## Assignment 2b

Now you can make an empty map of the Netherlands.

```{r} 
AddMapLayer(MapPlot(), map_municipal)

```

```{r}
#we used Addmaplayer to show an empty map of The Netherlands and its municipalities
```

## Assignment 2c

Read in the pc4 locations (nld_pc4_locations.csv).

Hint: Don't forget the X and Y should be numeric variables!

```{r}
pc4_locations <- read.csv2("../Downloads/nld_pc4_locations.csv") %>%
  mutate(X = as.numeric(as.character(X))) %>%
   mutate(Y = as.numeric(as.character(Y)))


str(pc4_locations)
```

```{r}
#Again we used read.csv2 to read the file. We then used mutate to represent X and Y and numeric values. 
```

## Assignment 2d

### 2di

Read in the school data

```{r}
schools <- read.csv2("../Downloads/schools.csv")

```

```{r}
#Again we used read.csv2 to read the file, and str to show the data of schools.
```

### 2dii

First, create a new dataframe schools1, which is equal to schools.

As you see POSTCODE has a structure of (1234 AB). You should create a new variable PC4 that is equal to the first 4 numbers in POSTCODE

Hint: Use the function `substr()`

Then select the variables PC4 and DENOMINATIE

```{r}
schools1 <- schools %>% mutate(PC4 = as.numeric(substr(POSTCODE, 1, 4))) %>% select(PC4, DENOMINATIE)%>% select(PC4, DENOMINATIE)
 schools1
  
```

```{r}
#We used mutate and substr to substract the last 2 letters of the postcode
```

### 2diii

Create the dataframe school_loc as a join from pc4_locations and school1 that combines the columns from both data frames, but only keeps rows where the value in the pc4_locations column matches in both data frames.
And then select the observations with DENOMINATIE is equal to "Rooms-Katholiek" or "Protestants-Christelijk"

```{r}
school_loc <- inner_join(schools1, pc4_locations, by= "PC4")
school_loc
```

```{r}
school_loc2 <- subset(school_loc, DENOMINATIE== "Rooms-Katholiek" | DENOMINATIE=="Protestants-Christelijk")
school_loc2

```

```{r}
#we used innerjoin to combine the schools postcode, type and location. Then we used subset to set apart the schools of type Rooms-Katholiek and Protestants-Christelijk.
```

## Assignment 2e

Create a map of Catholic and Protestant schools in the Netherlands


```{r}
AddMapLayer(MapPlot(),map_municipal) %>%
AddPointsLayer(school_loc2, columnNameColor="DENOMINATIE")


```

```{r}
#we used AddMapLayer to display the map of The Netherlands. Then we added AddPointsLayer to display the location of the Rooms-Katholieken and Protestants-Christenen
```

